Gelation as a condensation frustrated by hydrodynamics and mechanical tension

### 2014-08-27 gel_cond/trunk/generate.tex
Use aspect ratios rather than Porod exponent in fig:wholeprocess. Add labels for subfigures.

\begin{figure*}
	\tikzset{external/force remake}
	\tikzsetnextfilename{wholeprocess}
	\begin{tikzpicture}
	\begin{groupplot}[
	group style={
			group name=g, group size=1 by 2,
			vertical sep=3em,
			},
		width=0.4\textwidth,%
		height=0.2\textwidth+1em,%
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
		]
		\nextgroupplot[
			xlabel={time (min)},
			ymin=0, ymax=3, ylabel={Porod exponent},]
		\addplot[no marks, error bars/.cd, y dir=both,y explicit] table[y error index=2] {155C.porod};

@@

	\matrix[
		matrix of nodes, inner sep=0, column sep=0.0125\textwidth, row sep=0.5em,
		matrix anchor=north west,
		at={($(g c1r1.outer north east)+(-\textwidth,0)$)},
		] (m){
		\SI{5}{\minute} & \SI{10}{\minute} & \SI{20}{\minute} \\
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t024s.png}&
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t044s.png}&
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t084s.png}\\
		 \SI{30}{\minute} & \SI{40}{\minute} & \SI{50}{\minute}\\
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t00s.png}&
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t20s.png}&
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t40s.png}\\
		};

	\end{tikzpicture}
\caption{\textbf{Gelation observed in-situ} in a typical sample ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$). Origin of time is salt introduction. \textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters. \textbf{b} Evolution of Porod exponent. \textbf{c} Growth of the characteristic wave number. Time origin is shifted to correspond to the melting of the Wigner crystal.}
\label{fig:wholeprocess}
\end{figure*}

>>>>

\begin{figure*}
	\tikzset{external/force remake}
	\tikzsetnextfilename{wholeprocess}
	\begin{tikzpicture}[
		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
		]
	\begin{groupplot}[
	group style={
			group name=g, group size=1 by 2,
			vertical sep=3em,
			},
		width=0.4\textwidth,%
		height=0.2\textwidth+1em,%
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
		]
		\nextgroupplot[
			xlabel={time (min)}, xmin=0,
			ymin=0, ymax=1, ylabel={aspect ratio},
			only marks,]
		\addplot table {155C_percolation_1645.aspect} node[below left] {$\lambda_3/\lambda_1$};
		\addplot table[y index=3] {155C_percolation_1645.aspect} node[above left] {$\lambda_2/\lambda_1$};

@@

	\matrix[
		matrix of nodes, inner sep=0, column sep=0.0125\textwidth, row sep=0.5em,
		matrix anchor=north west,
		at={($(g c1r1.outer north east)+(-\textwidth,0)$)},
		] (m){
		\SI{5}{\minute} & \SI{10}{\minute} & \SI{20}{\minute} \\
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t024s.png}&
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t044s.png}&
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t084s.png}\\
		 \SI{30}{\minute} & \SI{40}{\minute} & \SI{50}{\minute}\\
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t00s.png}&
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t20s.png}&
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t40s.png}\\
		};
	\node[lab] at (m.north west) {a};
	\node[lab] at (g c1r1.outer north west) {b};
	\node[lab] at (g c1r2.outer north west) {c};
	\end{tikzpicture}
\caption{\textbf{Gelation observed in-situ} in a typical sample ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$). Origin of time is salt introduction. \textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters. \textbf{b} Evolution of average aspect ratios of cluster containing more than 4 particles. \textbf{c} Growth of the characteristic wave number. Time origin is shifted to correspond to the melting of the Wigner crystal.}
\label{fig:wholeprocess}
\end{figure*}
